\documentclass[../../main]{subfiles}
\begin{document}

\section*{ROS Packages for URDF, Gazebo, Navigation, and Communication}

% Start the longtable environment
\begin{longtable}{|>{\raggedright\arraybackslash}p{4cm}|>{\raggedright\arraybackslash}p{4cm}|p{7cm}|}
\caption{List of Useful ROS Packages for Robotics Development} \label{tab:ros_packages} \\

% Header for the first page
\hline
\textbf{Category} & \textbf{Package Name} & \textbf{Description} \\
\hline
\endfirsthead

% Header for subsequent pages
\multicolumn{3}{c}%
{{\tablename\ \thetable{} -- continued from previous page}} \\
\hline
\textbf{Category} & \textbf{Package Name} & \textbf{Description} \\
\hline
\endhead

% Footer for all pages except the last
\hline
\multicolumn{3}{r}{{Continued on next page}} \\
\endfoot

% Footer for the last page
\hline
\endlastfoot

% URDF Packages
URDF & urdf & Core package for defining robots in URDF format. \\
URDF & xacro & XML macro language for simplifying URDF files. \\
URDF & robot\_state\_publisher & Publishes the state of the robot to tf. \\
URDF & joint\_state\_publisher & Publishes joint states for simulating joint movements. \\
URDF & kdl\_parser & Parses URDF into KDL trees for kinematic calculations. \\
URDF & srdf & Semantic Robot Description Format for MoveIt!. \\

% Gazebo Packages
Gazebo & gazebo\_ros\_pkgs & ROS integration with Gazebo. \\
Gazebo & gazebo\_plugins & Plugins for sensors like cameras, lasers, and IMUs. \\
Gazebo & gazebo\_ros\_control & Integrates ROS control with Gazebo. \\
Gazebo & hector\_gazebo\_plugins & Additional plugins for GPS, sonar, and IMU sensors. \\
Gazebo & ros\_control & Framework for controlling robots in simulation and real hardware. \\
Gazebo & controller\_manager & Manages controllers for joints in Gazebo. \\
Gazebo & effort\_controllers & Effort-based controllers for joints. \\
Gazebo & position\_controllers & Position-based controllers for joints. \\
Gazebo & velocity\_controllers & Velocity-based controllers for joints. \\

% Navigation Packages
Navigation & move\_base & Core package for navigation stack, responsible for global and local path planning. \\
Navigation & amcl & Adaptive Monte Carlo Localization for 2D pose estimation. \\
Navigation & gmapping & SLAM algorithm using laser scans. \\
Navigation & cartographer & Advanced SLAM library supporting 2D and 3D mapping. \\
Navigation & navigation & Full ROS Navigation stack. \\
Navigation & global\_planner & Global path planner (e.g., A*, Dijkstra). \\
Navigation & local\_planner & Local path planner (e.g., DWA, TEB). \\
Navigation & teb\_local\_planner & Timed Elastic Band local planner for dynamic environments. \\
Navigation & costmap\_2d & 2D costmap representation for obstacle avoidance. \\
Navigation & dwa\_local\_planner & Dynamic Window Approach for local path planning. \\
Navigation & nav\_msgs & Messages related to navigation (e.g., Odometry, Path). \\

% Communication Packages
Communication & rospy & Python client library for ROS. \\
Communication & roscpp & C++ client library for ROS. \\
Communication & std\_msgs & Standard message types (e.g., Float32, String, Bool). \\
Communication & sensor\_msgs & Messages for sensor data (e.g., LaserScan, Image, Imu). \\
Communication & geometry\_msgs & Messages for geometry-related data (e.g., Pose, Twist, Point). \\
Communication & tf / tf2 & Transform library for managing coordinate frames. \\
Communication & actionlib & Action server/client for long-running tasks. \\
Communication & message\_filters & Synchronizes multiple topics based on timestamps. \\
Communication & rosserial & Communicate with microcontrollers over serial. \\
Communication & rosbridge\_suite & WebSocket-based communication for web-based interfaces. \\
Communication & rosapi & Provides REST API access to ROS topics, services, and parameters. \\

% Manipulation and Motion Planning Packages
Manipulation & moveit & Motion planning framework for robotic arms. \\
Manipulation & moveit\_core & Core components of MoveIt! (planning, kinematics, etc.). \\
Manipulation & moveit\_ros & ROS integration for MoveIt!. \\
Manipulation & moveit\_commander & Python interface for MoveIt!. \\
Manipulation & trac\_ik & Inverse Kinematics solver that works well with MoveIt!. \\
Manipulation & moveit\_visual\_tools & Tools for visualizing motion planning in RViz. \\
Manipulation & grasp\_generator & Generates grasps for robotic manipulators. \\

% Visualization Packages
Visualization & rviz & 3D visualization tool for ROS. \\
Visualization & rviz\_plugin\_tutorials & Tutorials for creating custom RViz plugins. \\
Visualization & rviz\_imu\_plugin & Plugin for visualizing IMU data in RViz. \\
Visualization & rviz\_satellite & Plugin for visualizing satellite imagery in RViz. \\

% Sensors and Perception Packages
Sensors & laser\_geometry & Converts laser scans into point clouds. \\
Sensors & image\_transport & Handles image transport (e.g., compressed images). \\
Sensors & camera\_info\_manager & Manages camera calibration information. \\
Sensors & depth\_image\_proc & Processes depth images (e.g., from RGB-D cameras). \\
Sensors & pcl\_ros & ROS integration with Point Cloud Library (PCL) for 3D perception. \\
Sensors & octomap & 3D occupancy grid mapping for collision avoidance. \\
Sensors & rtabmap\_ros & Real-Time Appearance-Based Mapping for SLAM. \\
Sensors & aruco\_ros & Detects ArUco markers for augmented reality and localization. \\

% Control and Dynamics Packages
Control & control\_toolbox & Provides PID controllers and other control utilities. \\
Control & realtime\_tools & Tools for real-time control in ROS. \\
Control & trajectory\_msgs & Messages for defining trajectories (e.g., JointTrajectory). \\
Control & joint\_trajectory\_controller & Controller for executing joint trajectories. \\
Control & gazebo\_ros\_force\_system & Applies forces to objects in Gazebo. \\

% Other Useful Packages
Other & dynamic\_reconfigure & Allows dynamic reconfiguration of node parameters at runtime. \\
Other & diagnostic\_updater & Monitors the health of ROS nodes and publishes diagnostic messages. \\
Other & robot\_localization & State estimation package that fuses data from multiple sensors. \\
Other & slam\_toolbox & Flexible SLAM solution with support for online and offline mapping. \\
Other & rosbag & Records and plays back ROS messages for debugging and testing. \\
Other & rosparam\_shortcuts & Simplifies loading parameters from the parameter server. \\

\end{longtable}

\end{document}